---
title: "datachallenge4"
author: "menglu zhao"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here are some tips:

First write a function that does one play of the Monty Hall simulation. Have an argument switch which tells if the contestant uses the strategy of switching the door (switch = TRUE) or (switch = FALSE).


Next use an if else statement to show what door is revealed if (1) the contestant guessed the correct door or (2) if the contestant did not guess the correct door
Use an if statement to switch guesses of the door if switch = TRUE
return a logical (TRUE/FALSE) indicating if the game was won or not

Next write a function that performs the simulation multiple times. Have an argument for the number of times to run the simulation (n) and the strategy (switch). Check out the replicate() function which may be useful.
Turn in an html of your R markdown document with the functions and a test of the functions with 1000 plays with/without using the switching strategy. Don’t forget to put your GitHub repo at the top of your R markdown!

```{r}
# if else statement to show which door is revealed 
door_to_reveal <- function(doors, prize_in_door, contestant_door) {
  if (prize_in_door == contestant_door) { # if the contestant's chosen door is the same as the prize door
    reveal <- sample(doors[-contestant_door], size = 1) # monty will reveal a goat from the remaining doors
  } else {
    reveal <- doors[-c(contestant_door, prize_in_door)] # monty will reveal the other door that has a goat
  }
  return(reveal)
}

# function that does one play of the Monty Hall simulation
play_monty_hall <- function(switch = FALSE) { # switch = false indicate the contestant does not want to switch doors
  doors <- 1:3 # three doors to choose from
  prize_door <- sample(doors, 1) # randomly assign the prize to a door
  contestant_door <- sample(doors, 1) # the door that contestant pick
  reveal <- door_to_reveal(doors, prize_door, contestant_door) # monty reveals a door which does not have the prize and was not picked by the contestant

  if (switch) {
    contestant_door <- setdiff(doors, c(contestant_door, reveal))
  }
  return (contestant_door == prize_door)  # return a logical (TRUE/FALSE) indicating if the game was won or not
}

```

